Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-09-06 Ben_Manuscripts/Paper1/Outline.tex
Modified intro

% BJC: Does it make sense to talk about metastable states? It was never really a goal to figure out other metastable states. 
  There remains the possibility that there is more than one metastable state 
  associated with a given LLC system.
  \begin{itemize}
    \item We must be able to identify which states can be produced experimentally
    and what implications each state might have regarding transport properties.
  \end{itemize}

>>>>

  There remains the possibility that there is more than one metastable state 
  associated with a given LLC system.
  \begin{itemize}
    \item Simulating a membrane atomistically will require many atoms which further
    limits the timescales acessible with MD
    \item It is reasonable to expect that we will generate configurations which 
    are kinetically trapped in a metastable free energy basin
    \item We must be able to identify which state is produced experimentally
  \end{itemize}
